%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}


%---------------------------------------------------------
  \cventrynew
    {Logichive Solutions Pvt Ltd., \textnormal{\textit{Graduate Engineer Trainee | Backend Intern} | Puttur, Karnataka, Ind}} % Job title
    {Jul 2023 - Present} % Date (s)
    {
      {\begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Developed {\bf SDKs} for {\bf 15+ APIs} in Python and Go, contributing to improved functionality and accessibility.}
          \item {Designed and implemented {\bf REST APIs} for an {\bf E-learning platform}, enhancing data exchange and platform connectivity.}
          \item {Contributed to the development of workspace solutions, virtual machines, and automated testing using {\bf Selenium}.}
          \item {Upload and Retrieval of Data from private mode {\bf Digital ocean space}.}
          \item {Implemented a Certification module using {\bf Pillow Python}, streamlining the certification process.}
          \item {Assisted in the {\bf indexing} of NoSQL databases, optimizing data retrieval and storage efficiency.}
          \item {Played a key role in the production and deployment processes, utilizing various {\bf DevOps} tools such as Docker and Swarm.}
          \item {Conducted {\bf unit and integration tests} on 50+ high-end APIs and SDKs, ensuring robust functionality and performance.}
    \end{cvitems}}
    }
    
%---------------------------------------------------------
  \cventrynew
    {Folkslogic Technologies \textnormal{\textit{UX Designer Intern} - Remote | Mangalore, Karnataka, Ind}} % Organisation
    % {} % Job title % Job title
    % {TamilNadu, India} % Location
    {Feb 2023 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created prototypes and mockups for various pixelated screens, using {\bf Figma} and {\bf Pencil} software , providing visual representations for design concepts.}
      \item {Contributed to animations, enhancing user experience and engagement on digital platforms.}
      \item {Engaged in photo and video editing tasks using {\bf Adobe} and {\bf Filmora}, ensuring high-quality multimedia content for projects.}
      \end{cvitems}
      }


%---------------------------------------------------------
  \cventrynew
    % {} % Organisation
    {Blueline Computers, \textnormal{\textit{Web Developing Intern} | Mangalore , Karnataka, Ind}} % Job title
    % {Bombay, India} % Location
    {Sep 2022 - Oct 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {Collaborated in creating and managing a relational database for an {\bf E-commerce website} with two other colleagues.}
  \item {Established an open-source {\bf GitLab} repository for code review and pipeline integration, fostering collaboration and version control.}
  \item {Presented and demonstrated the completed project as part of an academic subject in college.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries2}
